\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/ex.tex
abstract
example fonts
comment

\input{fig-ex-aby}

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-componenets. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend})\footnote{In our usage of ABY, boolean is synonymous
  with Yao (Section~\ref{sec:impl}).}.

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a_acc} and \ls{a_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.

@@

To summarize, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees. 
%% Consider a  cloud service provider Bob that wants to provide a service to diagnose
%% whether a patient has breast cancer or not. Bob trains a machine learning classification model
%% that results in a vector $w$ (say of length 30) and a scalar $b$.
%% This model is the intellectual property of Bob and he  wants to keep it secret.
%% Given a patient's medical report, in the form of a vector $x$ (also of length 30),
%% the classifer predicts that the patient has breast cancer if $w^Tx>b$.
%% However, for this task Bob needs access to $x$, which is private data of a customer.

>>>>

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby}\footnote{This is also how a program written directly in
  ABY would look like.}. shows the output code for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation

@@

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-componenets. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend}) (in our usage
of ABY, boolean is synonymous with Yao (Section~\ref{sec:impl})).

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.

\begin{figure}
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\text{{\color{red}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

$\mathtt{
for(uint32\_t\;i\;=\;0;\;i\;<\;30;\;i = i + 1)\;\{\;\;\text{\color{red}//acc = w}^{\text{{\color{red}T}}}\text{\color{red}x}~\label{line:dotproductloop}
}$
$\mathtt{
\;\;\;\;share\;*a\_t\_0 = acirc\rightarrow PutMULGate(a\_w[i], a\_x[i]);~\label{line:dotmulgate}
}$
$\mathtt{
\;\;\;\;a\_acc = acirc\rightarrow PutADDGate(a\_acc, a\_t\_0 );~\label{line:dotaddgate}
}$
$\mathtt{
\}
}$

//convert acc and b from arithmetic to boolean
$\mathtt{
share\;*y\_acc = ycirc\rightarrow PutA2YGate(a\_acc);~\label{line:convacc}
}$
$\mathtt{
share\;*y\_b = ycirc\rightarrow PutA2YGate(a\_b);~\label{line:convb}
}$

$\mathtt{
share\;*y\_pred = ycirc\rightarrow PutGTGate(y\_acc, y\_b);~\label{line:condyaobegin}
}$
$\mathtt{
uint32\_t\;one = 1;
}$
$\mathtt{
share\;*y\_1 = ycirc\rightarrow PutCONSGate(one, bitlen);
}$
$\mathtt{
uint32\_t\;zero = 0 ;
}$
$\mathtt{
share\;*y\_0 = ycirc\rightarrow PutCONSGate(zero, bitlen);
}$
$\mathtt{
share\;*y\_t = ycirc\rightarrow PutMUXGate(y\_pred, y\_1, y\_0);~\label{line:condyaoend}
}$

$\mathtt{
share\;*y\_out = ycirc\rightarrow PutOUTGate(y\_t, CLIENT);
}$
$\mathtt{
party\rightarrow ExecCircuit();
}$

$\mathtt{
if(role == CLIENT) \{\;\;\text{\color{red}//only to the client}
}$
$\mathtt{
\;\;\;\;uint32\_t \_o = y\_out\rightarrow get\_clear\_value\langle uint32\_t \rangle();
}$
$\mathtt{
\}
}$
\end{lstlisting}
\caption{\tool compiler (partial) output for Figure~\ref{fig:ex-sml}}
\label{fig:ex-aby}
\end{figure}

@@

To summarize, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees.

%% Consider a  cloud service provider Bob that wants to provide a service to diagnose
%% whether a patient has breast cancer or not. Bob trains a machine learning classification model
%% that results in a vector $w$ (say of length 30) and a scalar $b$.
%% This model is the intellectual property of Bob and he  wants to keep it secret.
%% Given a patient's medical report, in the form of a vector $x$ (also of length 30),
%% the classifer predicts that the patient has breast cancer if $w^Tx>b$.
%% However, for this task Bob needs access to $x$, which is private data of a customer.
